Light Transport Techniques for Tensor Field Visualization

### 2019-07-31 beamer2thesis/dummy.tex
update

\renewcommand\thempfootnote{\arabic{mpfootnote}}
\begin{document}

@@

\frame{
\frametitle{{Tensor Fields - Tensor Field Lines}}

\begin{columns}
\begin{column}{.6\textwidth}
\begin{small}
\begin{block}{\centering \textbf{Procedure}}
follow major/minor eigenvectors along pathlines
\end{block}
\end{small}
\bigskip
\begin{small}
\begin{itemize}
	\item ambiguity for nearly isotropic cases:\\ small changes in components effect large changes in tensor field line orientation (see Fig.)
	\item therefore susceptive to noise in data
	\item trajectories can cross each other\\
	$\Rightarrow$ effects erroneous trajectories, hard to interpret
\end{itemize}
\end{small}

\end{column}
\begin{column}{.4\textwidth}
\centering
\begin{figure}[t]
\centering
\includegraphics[height=0.8\textwidth]{nearly_isotropic.pdf}
\caption*{Ambiguity}
\end{figure}

>>>>

\setlength{\skip\footins}{0.1cm}
\setlength{\footnotesep}{0.1cm}
\renewcommand\thempfootnote{\arabic{mpfootnote}}
\begin{document}

@@

\frame{
\frametitle{{Propagation Scheme - Template}}
\begin{columns}
\begin{column}{.6\textwidth}
To interpret eigensystems of tensors as conductivity property for light transport, we will need a propagation scheme:\bigskip
\begin{itemize}
	\item using light propagation volumes (LPV) similar to Dachsbacher et al. (cf. Fig.)\bigskip
	\item exchanging itensities between neighboring cells: $\Phi_{t} = \int I(\omega)\mathop{d\omega}$\\
	{\small with $\Phi_{t}$: radiant flux, $I(\omega)$: radiant intensity}
\end{itemize}

\end{column}
\begin{column}{.4\textwidth}
\begin{figure}[t]
\centering
\begin{minipage}{0.79\textwidth}
\centering
\includegraphics[width=0.7\textwidth]{LPV.pdf}
\includegraphics[width=0.9\textwidth]{LPV2.pdf}
\caption*{Light Propagation Volumes}
\end{minipage}
\begin{minipage}{0.15\textwidth}
\source{\textit{A. Kaplanyan and C. Dachsbacher, ''Cascaded light}} 
\hspace{-3pt} {\tiny \raisebox{-0.75in}{\rotatebox[origin=t]{90}{propagation volumes for realtime indirect illumination"}}}
\end{minipage}
\end{figure}
